---
title: "Spatiotemporal Assessment of Risk and Risk Changes 
  for Rainfed Agriculture in Ethiopia (2000-2019)"
subtittle: Mini Report
author: "Oluwatosin Orenaike"
output: 
  html_document: 
    toc: yes
    theme: flatly
    toc_float: yes
    fig_caption: yes
    keep_md: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

This is a mini report on my thesis work on Spatiotemporal Assessment of Risk and Risk Changes for Rainfed Agriculture in Ethiopia. This is mainly for informative and showcasing the application of R and and it's GIS packages. 

The outline will include:
- An abstract
- The Methodology
- Results and script that generated the visuals

### An abstract

Drought in Ethiopia impacts agriculture severely. Previous drought assessments neglected the temporal dimension, hindering proper monitoring. A new assessment used composite indicators to analyze drought risk between 2000 and 2019, finding that the first half of the last two decades had more risk due to severe droughts and highly exposed croplands. The years 2000, 2002, and 2008 experienced major droughts. The study calls for a more dynamic drought risk management system in Ethiopia and global drought risk assessment.

```{r cars}
summary(cars)
```





```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## The Methodology

## Results and script that generated the vizuals